Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises

### 2022-09-28 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.tex
Sept 28 edits

\begin{figure}[H]
\caption{Case Study 1: Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
\centering{\includegraphics[height=19cm]{"./case_study_cuban_precision.png"}}
\end{figure}
\clearpage

@@

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Type\ (Episode\ or\ Event)}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{Start}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1945}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1977}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1995}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1993}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1989}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1816}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1816}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{End}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2019}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2018}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2020}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2010}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2015}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2014}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2007}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{\textbf{N}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{32K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{128K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1K}}} \\

>>>>

\begin{figure}[H]
\caption{Cuban Missile Crisis (1962) - ICB Narrative vs. ICBe Events \label{fig:case_study_cuban_precision}}
\centering{\includegraphics[height=19cm]{"./case_study_cuban_precision.png"}}
\end{figure}
\clearpage

@@

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Type\ (Episode\ or\ Event)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ep}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Ev}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Start}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1945}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1977}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1995}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1993}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1989}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1918}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1816}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1816}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{End}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2019}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2018}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2020}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2010}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2015}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2017}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2014}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{2007}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{N}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{32K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{8.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{28.4M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{17.5M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{9.6K}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{128K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{5.9K}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{1K}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Coders\ (Hand\ or\ Automated)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{A}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\cellcolor[HTML]{EFEFEF}\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{H}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 2pt}>{\centering}p{\dimexpr 0.1in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Corpus}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.6in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{ICB}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{News}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.22in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 2pt}}{\fontsize{6}{3}\selectfont{\textcolor[HTML]{000000}{Mix}}} \\
